\artus{} -- A Framework for Event-based Data Analysis in High Energy Physics

### 2015-11-17 Core/doc/latex/paper.tex

Especially new students joining the analysis groups can contribute very quickly.
Having understood general concept and structure of an \artus analysis, they can contribute by writing their own producers or filters while the full complexity of the event-processing is taken care of by the \artus framework.
In a similar manner, using the \artus framework, it is now much less work to set up a new analysis because a rich library of processors, filters and consumers exists and can be reused for new analyses.

>>>>

Especially new students joining the analysis groups can contribute very quickly.
Having understood general concept and structure of an \artus analysis, they can contribute by writing their own producers or filters while the full complexity of the event-processing is taken care of by the \artus framework.
Using the \artus framework, it is much less work to set up a new analysis because a rich library of processors, filters and consumers already exists and can be reused for new analyses.
